Topic and tone of political news articles in German online media.

### 2018-04-23 paper/docs/04_Modelresults_50.Rmd
change word count fig

library(igraph)
library(corrplot)
library(patchwork)
library(ggpmisc)
library(ggraph)
library(ggiraph)
library(tidygraph)
library(RColorBrewer) 
library(ggrepel)
library(scales)      # Scales

@@

ggsave(plot = {
  btw %>%
    ggplot(aes(as.numeric(text_length.cut),
                       group = site)) +
    geom_histogram(alpha=.8, fill = col[3]) + 
    scale_x_continuous(labels = c(seq(0,1500,500), ">2000")) +
    facet_wrap(~site, ncol = 4) +
    labs(x = "Word count", color = "") +
    theme(axis.title = element_text(size = 8),
          axis.text = element_text(size = 6))

>>>>

library(ggridges)
library(igraph)
library(corrplot)
#library(patchwork)
library(ggpmisc)
#library(ggraph)
library(ggiraph)
library(tidygraph)
library(RColorBrewer) 
library(ggrepel)
library(scales)      # Scales

@@

ggsave(plot = {
  btw %>%
    ggplot(aes(as.numeric(text_length.cut), site)) +
    geom_density_ridges(scale = 4,
                        fill = col[3], alpha = .8,
                        color = "white") +
    theme_ridges() +
    labs(x = "Word count", y = "") +
    scale_x_continuous(expand = c(0,0), 
                       labels = c(seq(0,1500,500), ">2000"))
